EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-14 draft.tex
Moving Sections

The trend concerning the parallel execution multi-population algorithms goes from
earlier hardware-based implementations using transputers
\cite{gorges1990explicit} through 
multi-core systems \cite{Serrano2008,lai2019adaptive} to multi-threaded \cite{merelo2019scaling} ones.
And recently the focus has been on exploiting a higher number of processing
units by using GPUs \cite{tan2015survey,li2007efficient}, or distributed
systems, including web-based \cite{JSON} systems,
map-reduce \cite{fazenda2012} implementations,  grids \cite{munawar2010design,Gonzalez09},
voluntary computing systems \cite{MilkyWay,merelo2016nodio}, 
and, more importantly, cloud computing
\cite{GValdez2015,salza2019speed,valenzuela2015implementing,FlexGP}. Cloud computing has become the standard way of running
enterprise applications, not only because of the convenience of the
pay-as-you-go model or the non-existent sunk cost of physical facilities, but also because
it offers a way of describing the infrastructure as part of the code, so that it
is much easier to reproduce results and this has been a boon for scientific
computing.  However,  cloud computing has also been evolving, going from simply
putting on virtual machines elsewhere than on premises old-style monolithic applications, that is, applications
built on a single stack of services that communicate by layers, to microservices
\cite{microservices} and serverless architectures \cite{varghese2018next,Varghese2018849} that favor the parallel and asynchronous communication of
heterogeneous resources; in the process, a new methodology for designing {\em cloud
native applications} has been created, with brand new methods and
techniques \cite{Baldini2016287}. In these architectures, services or even
functions are seen as independent processing nodes, departing from the monolithic
and even distributed paradigms, and becoming a loosely coupled collection of {\em
stateless functions} \cite{malawski2017serverless}, that react to events and
only come into existence while they are doing some processing.
Systems developed with the patterns outlined above have the
properties of a reactive system \cite{boner2014reactive} and they are commonly
more flexible, fault-tolerant, and scalable. % Some properies and reference - Mario  
% Again, you have to justify the need for a reactive architecture and define it before this paragraph - JJ

@@

We have proved this in the following steps:
% The reviewer says that we should clarify the contributions, and the
% contribution should answer a research question. Maybe we should
% clarify these contributions to answer to that. Contribution should
% be something like "We have proved that cloud-native applications are
% able to easily accommodate multi-paradigm bioinspired algorithms
% with little efforts of parametrization and
% that a combination of algorithms has better speedup and performance
% than any single one taken independently.
% These items above could be preceded by "We have proved this in the
% following steps" - JJ
% I like it will put it just like that. 
% A reviewer also put enph   asis on the workflow and reproductivility 
% and extracting a Model? we can put something on that too.
% yep.

@@

The organization of the paper is as follows: First, in Section \ref{multi}, we present a
background of the fundamental issues of integrating nature-inspired optimization
and multi-population methods. Section \ref{soa} presents state of the art relevant to
our work. In Section \ref{method}, we present the proposed method and the container-based
application in Section \ref{docker} and the workflow for experiment design in Section \ref{experiment_flow}. % No reference to section 6.
Section \ref{setup} describes
the design of the empirical evaluation we designed to assess the effectiveness
of the method, scalability is analysed in Section \ref{sec:exp1}, % This is a subsection, fix it. 
the performance of heterogeneous populations in Second \label{sec:exp2} 
and a cloud deployment example in Section \ref{cloud-aws}. % No references to sections 9 and 10
Finally, we
offer the conclusions of this paper and suggestions on future work in Section \ref{conclusions}.

@@

% a lot of this has been done in the previous method... Maybe there's
% not that much to do - JJ
% Hadoop 
%     Comparison \cite{ferrucci2018using}
%     Hadoop\cite{fazenda2012} 
%     FlexGP \cite{FlexGP}, 
%     elephant56 \cite{salza2016elephant56},

% Pool
%     SofEA \cite{merelo2012sofea,sofea:cec2012} , 
%     EvoSpace \cite{garcia2015evospace},
% Volunteer
%     evospace-js \cite{garcia2017evospace}
% Queue
%     Containers \cite{valenzuela2015implementing} \cite{salza2016approach} 
%     Seamless local and Cloud \cite{leclerc2016seamless}
%     Serverless KafKEO \cite{guervos2018introducing}, 
%     Docker Orchestation \cite{dziurzanski2020scalable,zhao2019cloud}
% PSO 
% PSO AWS \cite{li2015parallel}

@@

% Maybe you should say here how everything wors: launch with
% Docker-compose, whatever. That's the issue that one of the reviewers
% say - JJ

@@

% This is totally unexpected. Whose role is this? You didn't even introduce it. Also, extremely short - JJ
\subsection{Using the COCO Framework}

@@

\section{General Experimental Setup} 
\label{setup}

% Maybe subsection? Also say the question you're answering - JJ
\section{Measuring Scalability}
\label{sec:exp1}
% Experiment 1
As we mentioned before % say where - JJ
, reactive systems can scale by adding additional copies
of serverless functions. In our case, we can start additional worker containers
to have the same effect. Other authors, like Salza et al. \cite{salza2019speed},
have used a
similar architecture, which implies that worker nodes need to have at least a certain level
of complexity, in terms of execution time,  to effectively scale on multiple
nodes, tending to linear scalability. In that paper, Salza et al. tested scalability
by simulating the work of nodes by using a sleep function and messages of different sizes.
In a population-based algorithm like EvoSwarm, several parameters can increase or 
decrease the workload of workers:

\subsection{Setup}

\subsection{Experimental Results} 
\label{results}

% No idea where this fits in. I think it's the second question in 7, so it should probably be a subsection - JJ
\section{Performance of Heterogeneous Populations in the BBOB Benchmark}
\label{sec:exp2}

\subsection{Setup}

\subsection{Experimental Results}

\section{Deploying to a Cloud Provider}
\label{cloud-aws}
Container-based applications describe the deployment of loosely coupled
processes in a consistent and portable way, in every phase of the life cycle of
an application, from development through testing to production independently on
the kind of infrastructure. The term cloud-native describes these
container-based environments because they are deployed on an infrastructure that
abstracts the underlying compute, storage, and networking primitives. This
infrastructure does need to be a cloud provider; it could be a developer's
laptop, a single server, or a production environment. When we deploy a
cloud-native application to a cloud provider, we have some more options to
choose:

@@

\subsection{Setup}

@@

    controller:
      image: mariosky/controller
      command: python controller.py
      environment:
          PYTHONUNBUFFERED: 1
          REDIS_HOST: localhost
      logging:
        driver: awslogs
        options:
          awslogs-region: us-west-2
          awslogs-group: docker-logs
          awslogs-stream-prefix: controller
  \end{lstlisting}
% You will probably need to explain this a bit - JJ 
% done - M  
\subsection{Experimental Results}

@@

>>>>

The trend concerning the parallel execution multi-population algorithms goes from
earlier hardware-based implementations using transputers
\cite{gorges1990explicit} through 
multi-core systems \cite{Serrano2008,lai2019adaptive} to multi-threaded \cite{merelo2019scaling} ones.
And recently the focus has been on exploiting a higher number of processing
units by using GPUs \cite{tan2015survey,li2007efficient}, or distributed
systems, including web-based \cite{JSON} systems,
map-reduce \cite{fazenda2012} implementations,  grids \cite{munawar2010design,Gonzalez09},
voluntary computing systems \cite{MilkyWay,merelo2016nodio}, 
and, more importantly, cloud computing
\cite{GValdez2015,salza2019speed,valenzuela2015implementing,FlexGP}. Cloud computing has become the standard way of running
enterprise applications, not only because of the convenience of the
pay-as-you-go model or the non-existent sunk cost of physical facilities, but also because
it offers a way of describing the infrastructure as part of the code, so that it
is much easier to reproduce results and this has been a boon for scientific
computing.  However,  cloud computing has also been evolving, going from simply
putting on virtual machines elsewhere than on premises old-style monolithic applications, that is, applications
built on a single stack of services that communicate by layers, to microservices
\cite{microservices} and serverless architectures \cite{varghese2018next,Varghese2018849} that favor the parallel and asynchronous communication of
heterogeneous resources; in the process, a new methodology for designing {\em cloud
native applications} has been created, with brand new methods and
techniques \cite{Baldini2016287}. In these architectures, services or even
functions are seen as independent processing nodes, departing from the monolithic
and even distributed paradigms, and becoming a loosely coupled collection of {\em
stateless functions} \cite{malawski2017serverless}, that react to events and
only come into existence while they are doing some processing.
Systems developed with the patterns outlined above have the
properties of a reactive system \cite{boner2014reactive} and they are commonly
more flexible, fault-tolerant, and scalable. % Some properties and reference - Mario  
% Again, you have to justify the need for a reactive architecture and define it before this paragraph - JJ

@@

We have proved this in the following steps:
% The reviewer says that we should clarify the contributions, and the
% contribution should answer a research question. Maybe we should
% clarify these contributions to answer to that. Contribution should
% be something like "We have proved that cloud-native applications are
% able to easily accommodate multi-paradigm bioinspired algorithms
% with little efforts of parametrization and
% that a combination of algorithms has better speedup and performance
% than any single one taken independently.
% These items above could be preceded by "We have proved this in the
% following steps" - JJ
% I like it will put it just like that. 
% A reviewer also put enphasis on the workflow and reproducivility 
% and extracting a Model? we can put something on that too.
% yep.

@@

The organization of the paper is as follows: First, in Section \ref{multi}, we present a
background of the fundamental issues of integrating nature-inspired optimization
and multi-population methods. Section \ref{soa} presents state of the art relevant to
our work. In Section \ref{method}, we present the proposed method and the container-based
application in Section \ref{docker} and the workflow for reproducible experiment design in Section \ref{experiment_flow}. % No reference to section 6.
Section \ref{setup} describes the design of the empirical evaluation to assess the effectiveness
of the method,  with respect to scalability and % This is a subsection, fix it. 
the performance of heterogeneous populations.  % No references to sections 9 and 10
Finally, we offer the conclusions of this paper and suggestions on future work in Section \ref{conclusions}.

@@

@@

% Maybe you should say here how everything works: launch with
% Docker-compose, whatever. That's the issue that one of the reviewers
% say - JJ

@@

% This is totally unexpected. Whose role is this? You didn't even introduce it. Also, extremely short - JJ
% This is one of the applications described in the Workflow Figure. But this is better explained in other places.
% We can delete it (even from the Figure)  
% Will leave it until we decide - M 
\subsection{Using the COCO Framework}

@@

% TODO: connection to cloud subsection  - M

\subsection{Deploying to a Cloud Provider}
\label{cloud-aws}
Container-based applications describe the deployment of loosely coupled
processes in a consistent and portable way, in every phase of the life cycle of
an application, from development through testing to production independently on
the kind of infrastructure. The term cloud-native describes these
container-based environments because they are deployed on an infrastructure that
abstracts the underlying compute, storage, and networking primitives. This
infrastructure does need to be a cloud provider; it could be a developer's
laptop, a single server, or a production environment. When we deploy a
cloud-native application to a cloud provider, we have some more options to
choose:

@@

\subsubsection{Setup}

@@

    controller:
      image: mariosky/controller
      command: python controller.py
      environment:
          PYTHONUNBUFFERED: 1
          REDIS_HOST: localhost
      logging:
        driver: awslogs
        options:
          awslogs-region: us-west-2
          awslogs-group: docker-logs
          awslogs-stream-prefix: controller
  \end{lstlisting}
% You will probably need to explain this a bit - JJ 
% done - M  
\subsubsection{Experimental Results}

@@

\section{Experimental Study} 
\label{setup} % To be renamed

\subsection{General Experimental Setup} 
\label{sec:general-setup} % To be renamed

% Maybe subsection? Also say the question you're answering - JJ
\subsection{Measuring Scalability}
\label{sec:exp1}
% Experiment 1
As we mentioned before % say where - JJ
, reactive systems can scale by adding additional copies
of serverless functions. In our case, we can start additional worker containers
to have the same effect. Other authors, like Salza et al. \cite{salza2019speed},
have used a
similar architecture, which implies that worker nodes need to have at least a certain level
of complexity, in terms of execution time,  to effectively scale on multiple
nodes, tending to linear scalability. In that paper, Salza et al. tested scalability
by simulating the work of nodes by using a sleep function and messages of different sizes.
In a population-based algorithm like EvoSwarm, several parameters can increase or 
decrease the workload of workers:

\subsubsection{Setup}

%\subsubsection{Experimental Results} 
%\label{results}

% No idea where this fits in. I think it's the second question in 7, so it should probably be a subsection - JJ
\subsection{Performance of Heterogeneous Populations in the BBOB Benchmark}
\label{sec:exp2}

\subsubsection{Setup}

\subsubsection{Experimental Results}
